% !TEX program = xelatex
% !BIB program = bibtex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Modified by:
% Manuel Lagunas (http://webdiis.unizar.es/~mlagunas/)
% https://github.com/mlagunas/mlagunas-resume
% 
% COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{resume}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
 
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Manuel}{Lagunas}
{\href{mailto:mlagunas@unizar.es}{mlagunas@unizar.es}$\;$ 
-
$\;$\urlstyle{same}\href{http://webdiis.unizar.es/~mlagunas/}{webdiis.unizar.es/\textasciitilde mlagunas}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Zaragoza University}
\descript{MSc in Applied Mathematics}
\location{Sep 2017 | Zaragoza, Spain}
\location{Master thesis: 9.5/10}
\sectionsep

\subsection{Zaragoza University}
\descript{BS in Computer Science}
\location{Dec 2016 | Zaragoza, Spain}
\location{Bachelor project: 9.3/10}
\sectionsep

\subsection{Aarhus University}
\location{Jun 2015 | Aarhus, Denmark}
One year exchange programme.
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/mlagunas}{\bf mlagunas} \\
Stackoverflow://  \href{https://stackoverflow.com/users/6076729/manuel-lagunas?tab=profile}{\bf manuel-lagunas} \\
LinkedIn://  \href{https://www.linkedin.com/in/mlagunas/}{\bf mlagunas} \\
Twitter://  \href{https://twitter.com/mlagunas_}{\bf @mlagunas\_} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}

\subsection{Programming}
\location{Advanced:}
Python \textbullet{} Git \textbullet{} \LaTeX\ \textbullet{} SVN \\
% Matplotlib \textbullet{} PyTorch \textbullet{} Numpy
\location{Intermediate:}
C \textbullet{} C++ \textbullet{} CSS \textbullet{} HTML\\
Javascript \textbullet{} PHP\\
\location{Familiar:}
Android \textbullet{} MySQL \textbullet{} C\# \textbullet{} Java \\
\sectionsep

\subsection{Languages}
\textbf{Spanish} \textbullet{} Native speaker \\
\textbf{English} \textbullet{} Fluent \\
\textbf{French} \textbullet{} Basic \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Stochastic Processes \\
Machine Learning \\
Optimization Techniques \\
Evolutionary Computation \\
\sectionsep

\subsection{Undergraduate}
Artificial Intelligence \\
Computer Graphics \\
Compilers \\
Unix Tools and Scripting \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards} 
2016, NASA SpaceApps \\ $\;$\textbullet{} Best citizen-science project  \\
\vspace{0.15cm}
2015, Open Source Software Contest \\ $\;$\textbullet{} Finalist  

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Research Experience}

\runsubsection{Adobe Graphics Intelligence Lab}
\descript{| Research Intern}
\location{Jun 2019 – Current | San Jose, CA}
Working with \textbf{\href{http://sunxin.name/}{Xin Sun}} and \href{https://research.adobe.com/person/nathan-carr/}{\textbf{Nathan Carr}} on human capture and relighting.
\sectionsep

\runsubsection{Graphics and Imaging Lab}
\descript{| Zaragoza University, PhD in Machine Learning and Computer Graphics}
\location{Oct 2017 – Current (Sep 2021) | Zaragoza, Spain}
Working on the interface between machine learning and computer graphics. With a particular interest in the integration of machine learning into inverse rendering methods and in the intersection between human vision perception and machine learning. I am being supervised by \urlstyle{same}\href{http://giga.cps.unizar.es/~diegog/}{\textbf{Diego Gutierrez}} and \urlstyle{same}\href{http://webdiis.unizar.es/~bmasia/}{\textbf{Belen Masia}}.
\sectionsep

\runsubsection{Graphics and Imaging Lab}
\descript{| Undergraduate Researcher}
\location{Oct 2016 – Sept 2017 | Zaragoza, Spain}
Worked with \textbf{\href{http://www.elenagarces.es/}{Elena Garces}} on transfer learning and similarity problems in non-photorealistic domains (like cliparts or icons) while I was studying my bachelor´s and master´s degrees. This resulted in two publications: \textit{Learning Icons Appearance Similarity} and \textit{Transfer Learning for Illustration Classification}.
\sectionsep



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PUBLICATIONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Publications}
\nocite{*}
\printbibliography[heading=none]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     RESEARCH ACTIVITIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Research Activities}

\location{Deep Bayes Summer School | Aug 2019, Moscow, Russia}
Summer school on deep learning and bayesian methods.
\sectionsep

\location{DS3 Data Science Summer School | Jun 2019, Paris, France}
Summer school covering the latest advances in the field of data science.

\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Work Experience}

\runsubsection{Ibercentro Media}
\descript{| Software Engineering Intern}
\location{Jun 2015 – Oct 2015 | Zaragoza, Spain}
Software consulting company specialized in services for mass media companies. I created a tool for automatic fact extraction from spanish text leveraging natural language processing (NLP) tools.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     INDIVIDUAL PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Individual projects}

\location{Evolutionary Algorithms Library | Python + Numpy + Matplotlib}
High-level library that uses evolutionary strategies to solve numerical optimization problems with a modular structure that allows to easily implement new operators.

% It has a modular structure that makes easy to implement new operators for the selection, crossover, mutation, replacement operations or optimization functions.
\sectionsep

\location{PyTorch np-transforms | Python + PyTorch + Numpy}
PyTorch image transforms based on Numpy instead of the default Python Imaging Library. It includes support for HDR images, adds new transforms and filters.

\end{minipage} 
\end{document}  \documentclass[]{article}
